Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-18 WRITEUP/ms.tex
Updates from Overleaf

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{Probability distribution function of the H$_2$ number density in \flower during the accretion phase shown in \Fig{SFH}.
\label{fig:h2density}}
\end{figure}

@@

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation relates MCs structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}. This is also known as the constant column density relation, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with MW-like dust can be written as 
\begin{equation}
A_v = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
then, assuming spherical symmetry, the mass of a MC can be expressed as a function of $A_v$ and its size $l$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n l^3 = 154 \,A_v \left(\frac{l}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we have taken $\mu = 2.5$ as the mean molecular weight.

We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
%
In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$. As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus of $A_v \simeq 8.9$ clouds observed by \citet{Lombardi10a} in the MW.
%
% use bla

%
The values of $A_V$ inferred from http://adsab%s.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

% mass-size relation
In terms of the mass-size relation (\Fig{MR}), the MCs of \flower are found to lie above the \citet{Kauffmann10c} relation, which is an empirical relation corresponding to the threshold for massive \SF, but lies
%The implication of this \citet{Kauffmann10c} relation is that cluster-forming cloud fragments are
%found to be more massive than those that are devoid of clusters
%at a given radius.
below the locus of $A_V$\eq100\,mag followed by Milky Way clouds. This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MC within each cell in our simulation.}.
%
That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.

% different evolutionary stages
In the scaling relations examined, we find similar MC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}). That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr.

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/hist_test_16.pdf}
\caption{Probability distribution function of the H$_2$ number density in \flower during the accretion phase shown in \Fig{SFH}.
\label{fig:h2density}}
\end{figure}

@@

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation relates MCs structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}. This is also known as the constant column density relation, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with MW-like dust can be written as 
\begin{equation}
A_v = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
then, assuming spherical symmetry, the mass of a MC can be expressed as a function of $A_v$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154 \,A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we have taken $\mu = 2.5$ as the mean molecular weight.

We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
%
In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$. As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus of $A_v \simeq 8.9$ clouds observed by \citet{Lombardi10a} in the MW.
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

@@

% mass-size relation
MCs of \flower lie below the locus of $A_V$\eq100\,mag followed by Milky Way clouds in the mass-size relation shown in \Fig{MR}. This can be understood by acknowledging the fact that a H$_2$ molecular cloud does not necessary contain CO (e.g., as CO forms deeper in molecular clouds), and that our simulation does not have enough resolution to directly form CO\footnote{In fact, to form CO and make predictions for CO line emission in the work presented by \citet{Vallini18a}, we model the internal structure of MC within each cell in our simulation.}.
%
That is, the MCs of \flower lying along the locus of $A_V$\eq4\,mag likely manifests from the fact that the MCs in our simulation have lower column densities than the star-forming cores observed in the Milky Way, which are observationally well-resolved within an MC, and indeed, have sufficient column density to form CO.

The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow 
an ``internal'' mass-size relation where $M\propto r^{1.33}$.
If this holds for MCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
regions of high-mass \SF. That is, the MCs identified have mass-size relations suggesting they are capable of high-mass \SF.

% different evolutionary stages
In the scaling relations examined, we find similar MC properties in relation to those observed in the nearby Universe between the accretion phase and the starburst phase of \flower (see \Fig{larsons_single}). That is, we do not find any quantitative major differences in the MC properties between the accretion and the starburst phase, which are separated by $\simeq$300\,Myr. \DL{some MCs in SB phase have
lower $\alpha_{\rm vir}$ and pressure, but 
is there any significance in that?}
